Analysis of split plot design using MCMCglmm

### 2020-05-19 README.Rmd
fix another link in README
Update name of package

Once the download is complete, open the `rice.awd.pests.Rproj` in RStudio to
begin working with the package and compendium files.

@@

    docker run -dp 8787:8787 adamhsparks/rice-awd-pests

>>>>

Once the download is complete, open the `rice.awd.shb.Rproj` in RStudio to
begin working with the package and compendium files.

@@

    docker run -dp 8787:8787 adamhsparks/rice_AWD_ShB_analysis
